A Closer Look at Time-Preserving Paths on Evolving Graphs

### 2018-03-19 paper.tex
add more contents

\section{Background}
\label{sec:preliminaries}

Let $G$ be a directed graph with $n$ nodes with the corresponding adjacency matrix
$A \in \R$.

A \textbf{walk} of length $r$ from node $i_1$ to node $i_{r+1}$ is a sequence of edges
$(i_1, i_2), (i_2, i_3), \ldots (i_r, i_{r+1})$.

\subsection{Graph Centrality}
\label{sec:katz-centrality}

% definition of various graph centrality algorithms
We review the Katz centrality here.
Let $A$ be the adjacency matrix of a graph $G=(V,E)$ and $\rho(A)$ be the spectral radius of $A$. If $\alpha < 1/ \rho(A)$, then the Katz centrality vector of $G$ is
\[
(I - \alpha A)^{-1}e.
\]

The \emph{betweenness centrality} of a node $i$ in a static graph is defined as
$$
C_i = \sum_{j \in V}\sum_{k \in V, k \ne j} \frac{\rho_{jk}(i)}{\rho_{jk}},
$$
where $\rho_{jk}$ is the number of shortest paths from node $j$ to node $k$, while $\rho_{jk}(i)$ is the number of shortest paths from node $j$ to node $k$ that pass through node $i$

@@

@@

% \subsubsection{Aggregated Graphs and Evolving Graphs}
% \label{sec:aggr-graphs-evolv}

>>>>

% \section{Background}
% \label{sec:preliminaries}
%
% Let $G$ be a directed graph with $n$ nodes with the corresponding adjacency matrix
% $A \in \R$.
%
% A \textbf{walk} of length $r$ from node $i_1$ to node $i_{r+1}$ is a sequence of edges
% $(i_1, i_2), (i_2, i_3), \ldots (i_r, i_{r+1})$.
%
%
% \subsection{Graph Centrality}
% \label{sec:katz-centrality}
%
% % definition of various graph centrality algorithms
% We review the Katz centrality here.
% Let $A$ be the adjacency matrix of a graph $G=(V,E)$ and $\rho(A)$ be the spectral radius of $A$. If $\alpha < 1/ \rho(A)$, then the Katz centrality vector of $G$ is
% \[
% (I - \alpha A)^{-1}e.
% \]
%
% The \emph{betweenness centrality} of a node $i$ in a static graph is defined as
% $$
% C_i = \sum_{j \in V}\sum_{k \in V, k \ne j} \frac{\rho_{jk}(i)}{\rho_{jk}},
% $$
% where $\rho_{jk}$ is the number of shortest paths from node $j$ to node $k$, while $\rho_{jk}(i)$ is the number of shortest paths from node $j$ to node $k$ that pass through node $i$

@@

The Katz Centrality is a measure of importance

@@

\subsection{Paper Subject Tag Network}

We tag our research articles by subjects. The subjects re provided by ACM Computing Classification System (also contains the superclass and subclass).

We can construct a time-dependent tag network by link tags in each articles. For example,
suppose a paper $p_1$ has three tags $t_1$, $t_2$, and $t_3$, where $t_1$ is a superclass of $t_2$ and $t_3$.
We link $t_2$ and $t_3$ in both direction and create a link from $t_1$ to $t_2$ and a link from $t_1$ to $t_3$.
The time stamp of these edges is the published date of the paper.
